NumPy---Array Programming in Python

### 2020-01-16 body.tex
Fix typo

Many of these functions, such as summation, support reductions: aggregating
results across over or more dimension of the array.
For example, summing a $D$-dimensional array over $p$ axes results in a
$D-p$-dimensional array (Fig.~\ref{fig:array-concepts}e).

>>>>

Many of these functions, such as summation, support reductions: aggregating
results across one or more dimensions of the array.
For example, summing a $d$-dimensional array over $c$ axes results in a
$(d-c)$-dimensional array (Fig.~\ref{fig:array-concepts}e).
